### 2023-03-07 README.Rmd
`usethis::use_tidy_logo()`

# infer R Package <img src="man/figures/infer.png" align="right" width=280 />

@@

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("tidymodels/infer")
```

>>>>

# infer R Package <img src="man/figures/logo.png" align="right" width=280 />

@@

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("tidymodels/infer")
```
